---
output:
  html_document:
    fig_height: 3
    fig_width: 3.5
    keep_md: yes
---

See the Rmd file here: https://raw.githubusercontent.com/ralfer/apa_format_and_misc/master/example/example.Rmd

```{r, cache=F}
library(apastats)
load.libs(c('data.table','knitr'))
opts_chunk$set(message=F)
```
```{r}
t_res<-t.test(rnorm(20, mean = 10, sd=2))

t_res
```

One sample Student's t-test demonstrated that X significantly higher than zero, `r describe.ttest(t_res)`.

```{r}
data("sleep")
describe.mean.and.t(sleep$extra, sleep$group, which.mean = 3, paired=T)

```

Student's t-test showed that increase in hours of sleep compared to control was lower in group 1 than in group 2, `r with(sleep, describe.mean.and.t( extra, group,which.mean = 3, paired=T))`. 


```{r}
require(MASS)
glm_res<-glm(Freq ~ (Age+Sex)*Survived, family = poisson, data = data.frame(Titanic))

describe.glm(glm_res)

lm_res<-lm(Postwt ~ Prewt + Treat + offset(Prewt), anorexia)
describe.glm(lm_res)
```

```{r}
describe.glm(glm_res, "SexFemale:SurvivedYes", dtype=1)
describe.glm(glm_res, "SexFemale:SurvivedYes", dtype=2)
describe.glm(glm_res, "SexFemale:SurvivedYes", dtype=3)
describe.glm(glm_res, "SexFemale:SurvivedYes", dtype=3, test.df=T)
```

Adults had lower chances of survival on Titanic than children, `r describe.glm(glm_res, "AgeAdult:SurvivedYes")`, and women had higher chances than men, `r describe.glm(glm_res, "SexFemale:SurvivedYes", dtype=3)`. 

```{r}
require(ez)
data(ANT)

rt_anova = ezANOVA(
    data = ANT[ANT$error==0,]
    , dv = rt
    , wid = subnum
    , within = .(cue,flank)
    , between = group
)

rt_anova
```

Repeated measures ANOVA demonstrated a significant influence of cue on RT, `r describe.ezanova(rt_anova, 'cue')`. 

### Plotting pointrange plots

You can plot within-subject CIs with the help of summarySEwithin from http://www.cookbook-r.com/Graphs/Plotting_means_and_error_bars_%28ggplot2%29/

```{r, pointrange_plots, message=F, cache=F}
require(nlme)
require(gridExtra)

data(ergoStool)

p1 <- plot.pointrange(ergoStool, aes(x = Type, y = effort)) +
  labs(x = "Stool type", y = "Effort", title = "Usual CIs")
p2 <- plot.pointrange(
  ergoStool,
  aes(x = Type, y = effort),
  within_subj = TRUE,
  wid = "Subject"
) +
  labs(x = "Stool type", y = "Effort", title = "Within-subject CIs")
grid.arrange(p1, p2, ncol=2)
```

### Showing log-transformed data back untransformed

Sometimes it is useful to analyze data log-transformed, but show the axis in the original units. `scale_y_exp()` is useful for this.

```{r}
mtcars$log_mpg <- log(mtcars$mpg)

p0 <- plot_pointrange(
  mtcars,
  aes(x = factor(cyl), y = log_mpg)
) + labs(x = "Cylinders", y = "Log mpg")

p0

p1 <- plot_pointrange(
  mtcars,
  aes(x = factor(cyl), y = log_mpg)
) +
  scale_y_exp(digits = 1) +
  labs(x = "Cylinders", y = "Miles per gallon")

p1
```

The maintained package vignette, `vignette("apastats2-intro")`, contains the current examples.
