```{r}
source('../functions.R', chdir=T)

t_res<-t.test(rnorm(20, mean = 10, sd=2))

t_res
```

One sample Student's t-test demonstrated that X significantly higher than zero, `r describe.ttest(t_res)`.

```{r}
with(sleep, describe.mean.and.t( extra, group, which.mean = 3, paired=T))

```

Student's t-test showed that increase in hours of sleep compared to control was lower in group 1 than in group 2, `r with(sleep, describe.mean.and.t( extra, group,which.mean = 3, paired=T))`. 


```{r}
require(MASS)
glm_res<-glm(Freq ~ (Age+Sex)*Survived, family = poisson, data = data.frame(Titanic))

describe.glm(glm_res)

lm_res<-lm(Postwt ~ Prewt + Treat + offset(Prewt), anorexia)
describe.glm(lm_res)
```

```{r}
describe.glm(glm_res, "SexFemale:SurvivedYes", short=1)
describe.glm(glm_res, "SexFemale:SurvivedYes", short=2)
describe.glm(glm_res, "SexFemale:SurvivedYes", short=3)
describe.glm(glm_res, "SexFemale:SurvivedYes", short=3, test_df=T)
```

Adults had lower chances of survival on Titanic than children, `r describe.glm(glm_res, "AgeAdult:SurvivedYes")`, and women had higher chances than men, `r describe.glm(glm_res, "SexFemale:SurvivedYes", short=3)`. 

