---
title: "Getting Started with apastats2"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with apastats2}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`apastats2` provides helpers for formatting statistical results in APA style.
This vignette shows a minimal workflow using base datasets and core functions.

## Format test results

```{r}
library(apastats2)

set.seed(1)
t_res <- t.test(rnorm(20, mean = 10, sd = 2))
t_str <- apa(t_res)
t_str
```

Inline rendering example: One-sample test result was `r t_str`.

```{r}
data("sleep")
mt_str <- apa_mean_and_t(sleep$extra, sleep$group, which.mean = 3, paired = TRUE)
mt_str
```

Inline rendering example: Sleep increase comparison was `r mt_str`.

```{r}
set.seed(2)
x <- rnorm(40)
y <- 0.5 * x + rnorm(40, sd = 0.8)
cor_str <- apa(cor.test(x, y))
cor_str
```

Inline rendering example: Correlation result was `r cor_str`.

```{r}
tbl <- matrix(c(30, 20, 15, 35), nrow = 2, byrow = TRUE)
chi_str <- apa(chisq.test(tbl))
chi_str
```

Inline rendering example: Chi-square result was `r chi_str`.

## Format model terms

You can format selected terms from linear or generalized models.

```{r}
glm_res <- glm(Freq ~ (Age + Sex) * Survived, family = poisson, data = data.frame(Titanic))
glm_str <- apa(glm_res, term = "SexFemale:SurvivedYes", dtype = 3)
glm_str
```

Inline rendering example: GLM term result was `r glm_str`.

## Confidence intervals for repeated-measures summaries

`get_superb_ci()` computes summary statistics and interval columns suitable for plotting.

```{r, eval = requireNamespace("superb", quietly = TRUE)}
data(faces)
ci_data <- get_superb_ci(faces, "uid", "stim_gender", "answerTime")
ci_data[, c("stim_gender", "descr")]
```

```{r, eval = !requireNamespace("superb", quietly = TRUE)}
cat("Package 'superb' is not installed; skipping within-subject CI example.\n")
```

## Point-range plotting

`plot_pointrange()` can be used directly for quick summaries.

```{r, fig.width=5, fig.height=3, eval = requireNamespace("superb", quietly = TRUE)}
plot_pointrange(
  faces[correct == 1, ],
  aes(x = user_gender, color = stim_gender, y = answerTime),
  wid = "uid",
  within_subj = TRUE,
  withinvars = c("stim_gender"),
  betweenvars = c("user_gender")
)
```

## Misc helpers

```{r}
round_p(c(0.025, 0.0001, 0.568))
mean_ci_str <- apa_mean_conf(c(1.1, 1.5, 0.9, 1.8, 1.2), bootCI = FALSE)
mean_ci_str
```

Inline rendering example: Mean and CI summary was `r mean_ci_str`.

See individual help pages for full argument details and supported model classes.
